Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-25 robdml.tex
tex

@@

In Deep Metric Learning (DML)~\cite{revisiting,dmlreality}, an embedding
function $\phi:\mathcal{X}\mapsto \Phi \subseteq \mathbb{R}^D$ is learned to
map data points $X\in\mathcal{X}$ into an embedding space $\Phi$, where the
output of $\phi(\cdot)$ is usually normalized to the real unit hypersphere for
regularization purpose.
%
With a predefined distance function $d(\cdot,\cdot)$, it allows us to measure
the distance between $X_i$ and $X_j$ as
$d_\phi(X_i,X_j)=d(\phi(X_i),\phi(X_j))$.
%
Various loss functions for learning the underlying embedding function have been
proposed~\cite{revisiting,dmlreality}, where the triplet loss~\cite{facenet}
remain to be a strong and widely used baseline that could reach
state-of-the-art performance with appropriate triplet sampling strategy.
%
Given a triplet of image embeddings (anchor $\va=\phi(X_a)$, positive sample
$\vp=\phi(X_p)$, negative sample $\vn=\phi(X_n)$), the triplet loss is defined
as:
%
$
%
	L_\text{T}(\va, \vp, \vn; \gamma) = \max(0, d(\va, \vp) - d(\va, \vn) +
	\gamma),
%
$
%
where $\gamma$ is a predefined margin parameter.

>>>>

In Deep Metric Learning (DML)~\cite{revisiting,dmlreality}, an embedding
function $\phi:\mathcal{X}\mapsto \Phi \subseteq \mathbb{R}^D$ is learned to
map data points $X\in\mathcal{X}$ into an embedding space $\Phi$, which is usually
normalized to the real unit hypersphere for regularization.
%
With a predefined distance function $d(\cdot,\cdot)$, which is usually the
Euclidean distance, we can measure the distance between $X_i$ and $X_j$ as
$d_\phi(X_i,X_j)=d(\phi(X_i),\phi(X_j))$.
%
In a typical setting, the triplet loss~\cite{facenet} can be used to learn the
embedding function, and it could reach the state-of-the-art performance with an
appropriate triplet sampling strategy~\cite{revisiting}.

Given a triplet of image embeddings (anchor $\va=\phi(X_a)$, positive sample
$\vp=\phi(X_p)$, negative sample $\vn=\phi(X_n)$), the triplet loss is defined
as:
%
$
%
	L_\text{T}(\va, \vp, \vn; \gamma) = \max(0, d(\va, \vp) - d(\va, \vn) +
	\gamma),
%
$
%
where $\gamma$ is a predefined margin parameter.

@@
